Preprocessing summary

### 2016-04-02 inst/examples/summary.Rmd
ok

```{r summary-conversions, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=15}
field.conversions <- cbind(harmonize_field_names(), preprocessed = unname(sapply(conversions, function (x) {paste(x, collapse = ";")})[as.character(harmonize_field_names()$name)]))
names(field.conversions) <- c("marc_clearname", "marc_field", "preprocessed_fields")
field.conversions <- field.conversions[, c(2, 1, 3)]
kable(field.conversions)
```

>>>>

```{r summary-conversions, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=15}
a <- harmonize_field_names()
b <- sapply(conversions, function (x) {paste(x, collapse = ";")})
coms <- intersect(as.character(a$name), names(b))

field.conversions <- cbind(a[match(coms, a$name), ], preprocessed = unname(b[coms]))
names(field.conversions) <- c("marc_clearname", "marc_field", "preprocessed_fields")
field.conversions <- field.conversions[, c(2, 1, 3)]
kable(field.conversions)
```
